\bibitem{veltman}Veltman, M.J.G. and Williams, D.N. (1991). 'Schoonschip ’91.'\label{Ref: veltman}
\bibitem{maple}Lopez, R. \textit{Computer Algebra Systems.} Maplesoft, viewed 26 November 2019. \url{https://www.maplesoft.com/ns/maple/cas/computer-algebra-systems-math-education.aspx}.\label{Ref: maple}
\bibitem{computeralgebra}Güyer, T. (2008). 'Computer Algebra Systems as the Mathematics Teaching Tool.' \textit{World Applied Sciences Journal} 3 (1): 132-139, 2008.\label{Ref: computeralgebra}
\bibitem{wz}Wilf, H.S., and Zeilberger, D. (1990). 'Rational functions certify combinatorial identities.' \textit{J. Amer. Math. Soc. 3} (1990), pp. 147–158.\label{Ref: wz}
\bibitem{mathematica}Paule, P. and Schorn, M. (1994). 'A Mathematica Version of Zeilberger's Algorithm for Proving Binomial Coefficient Identities.' \textit{J. Symbolic Computation} (1995) 20, pp. 673--698.\label{Ref: mathematica}
\bibitem{wilf}Wilf, H.S. (1994). \textit{Generating functionology.} Academic Press, Inc. Philadelphia, Pennsylvania.\label{Ref: wilf}
\bibitem{gosper}Gosper, R.W. Jr. (1978). \textit{Decision procedure for indefinite hypergeometric summation.} Proc. Natl. Acad. Sci. USA. Vol. 75, No. 1, pp. 40--42, January 1978. Palo Alto, California.\label{Ref: gosper}
\bibitem{parser}Johnson, M. (2007). \textit{Handout 08 Bottom-up Parsing.} Lecture notes Stanford University CS143. Delivered 2 July 2007. \url{https://web.archive.org/web/20160305041504/http://dragonbook.stanford.edu/lecture-notes/Stanford-CS143/08-Bottom-Up-Parsing.pdf}\label{Ref: parser}
\bibitem{gould}Gould, H.W. (1972). \textit{Combinatorial Identities.} Morgamtown Printing and Binding Co. West Virginia.\label{Ref: gould}
\bibitem{tesler}Tesler (2017). \textit{Chapter 3.3, 4.1, 4.3. Binomial Coefficient Identities.} Lecture notes University of California San Diego Math 184A. Delivered winter 2019. \url{http://www.math.ucsd.edu/~gptesler/184a/slides/184a_ch4slides_19-handout.pdf}\label{Ref: tesler}
